---
title: "HW6"
author: "Makana Burch"
date: "2024-10-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploring Overpass API

In order to obtain data on the businesses near BlueBike stations, I want to use Overpass, which I've used in Python before. This is an exploration of using Overpass in R. 

# Downloading and loading packages

```{r}
library(httr)
library(jsonlite)
```
# Testing an existing query for Overpass

This query searches for schools within one mile of 42.3601, 71.0589 (Boston) and prints the results. 

```{r}
lat = 42.3601
lon = -71.0589

overpass_url = "http://overpass-api.de/api/interpreter"

query = sprintf(
  '[out:json];
    (
        node["amenity"="school"](around:1609,%s,%s);
        way["amenity"="school"](around:1609,%s,%s);
        relation["amenity"="school"](around:1609,%s,%s);
    );
    out center 100;', lat, lon, lat, lon, lat, lon
)

response = POST(overpass_url, body = list(data = query), encode = "form")

if (response$status_code == 200) {
  result = content(response, "text")
  json_parsed = fromJSON(result)
} else {
  stop("Error")
}

print(json_parsed)
```
## Converting the result into a dataframe

```{r}
if (length(json_parsed$elements) > 0) {
  extracted_data = json_parsed$elements
}

place_lat = c()
place_lon = c()
place_name = c()
place_type = c()


for (i in 1:length(extracted_data[,1])) {
  
  if (!is.na(extracted_data[,3][i])) {
    place_lat = c(place_lat, extracted_data[,3][i])
  } else if (extracted_data[,6]['lat'][i,] != "NA") {
    place_lat = c(place_lat, extracted_data[,6]['lat'][i,])
  } else {
    place_lat = c(place_lat, NA)
  }
  
  if (!is.na(extracted_data[,4][i])) {
    place_lon = c(place_lon, extracted_data[,4][i])
  } else if (extracted_data[,6]['lon'][i,] != "NA") {
    place_lon = c(place_lon, extracted_data[,6]['lon'][i,])
  } else {
    place_lon = c(place_lon, NA)
  }
  
  if (!is.null(extracted_data[,5]['name'][i,])) {
    place_name = c(place_name, extracted_data[,5]['name'][i,])
  } else {
    place_name = c(place_name, NA)
  }
  
  if (!is.null(extracted_data[,5]['amenity'][i,])) {
    place_type = c(place_type, extracted_data[,5]['amenity'][i,])
  } else {
    place_type = c(place_type, NA)
  }
}

df = data.frame(
  Name = place_name,
  Latitude = place_lat, 
  Longitude = place_lon, 
  Type = factor(place_type),
  stringsAsFactors = FALSE
)

summary(df)

```


